Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/motivation.tex
make spell

We found 83 vulnerabilities in the CVE database~\cite{cve-database}
that mention the search string ``ZIP.''  Just 16 of these vulnerabilities
were related to processing ZIP archives; the rest were unrelated to ZIP
archives or involved applications insecurely using the contents of untrusted
ZIP files.  Figure~\ref{fig:motivation} summarizes the 16 ZIP-related
vulnerabilities.

>>>>

We found 83 vulnerabilities in the CVE database~\cite{cve-database}
that mention the search string ``ZIP\@.''  Just 16 of these vulnerabilities
were related to processing ZIP archives; the rest were unrelated to ZIP
archives or involved applications insecurely using the contents of untrusted
ZIP files.  Figure~\ref{fig:motivation} summarizes the 16 ZIP-related
vulnerabilities.
